---
header-includes:
- \usepackage[table]{xcolor}
- \usepackage{amsmath}
- \usepackage{xcolor}
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{fancyhdr}
- \usepackage{lipsum}
- \AtBeginDocument{\let\maketitle\relax}
Output: 
  pdf_document:
  toc: false
sansfont: Calibri Light
documentclass: report
geometry: margin=2.0cm
#classoption: landscape
---
  
```{r setup, echo=FALSE}
options(tinytex.verbose = TRUE)
options(knitr.table.format = "latex")
suppressWarnings(suppressPackageStartupMessages(library(dplyr)))
suppressWarnings(suppressPackageStartupMessages(library(DT)))
suppressWarnings(suppressPackageStartupMessages(library(stringr)))
library(dplyr)
library(knitr)
library(rmarkdown)
#library(xtable)
library(kableExtra)
library(formattable)
```


```{r load, include=FALSE}
load(file = "my-dt.Rdata")
```
```{r total, echo=FALSE}
# sub set data for the current facilty 
#paste("building name:",blt_nm,sep = " ")
rpt_data <- rt[rt$Building.name==blt_nm,]



total <- round(sum(rpt_data$Client.Rate),2)
#total <- as.character(total)
total <- currency(total, digits = 2L)

rpt_data$Client.Rate <- currency(rpt_data$Client.Rate, digits = 2L)                               # prepare currency format 

```


\pagestyle{fancy}
\fancyhead[CO,CE]{Vancouver Island Health Authority}
\fancyfoot[CO,CE]{`r format(Sys.time(), tz="America/Los_Angeles",usetz=TRUE)`}
\fancyfoot[LE,RO]{\thepage}



\newpage
\vspace*{160px}
\begin{center}
\fontfamily{cmr}
\fontsize{18}{28}
\selectfont
\textcolor{red}{Vancouver Island Health Authority}      

\fontfamily{cmr}
\fontsize{18}{28}
\fontseries{b}
\selectfont
\bigbreak
\line(1,0){440}
\newline
\textcolor{red}{Assisted Living BILLING ACTIVITY REPORT}   
\line(1,0){380}

{\ttfamily
\fontsize{12}{12} 
\hspace*{3ex}\hspace{4ex}\textcolor{black}{`r blt_nm`}  
}
\newline  
\fontsize{10}{10} 
\textcolor{black}`r format(Sys.time(), "%B %d, %Y")` 

\vspace{4 cm}

\end{center}

\newpage

\vspace*{10px}
\fontfamily{cmr}
\fontsize{14}{80}
{\ttfamily
\hspace*{3ex}\hspace{10ex}\hspace{1ex}\textcolor{red}{ASSISTED LIVING FACILTY BILLING ACTIVITY REPORT} 
}
\newline
\newline

\textcolor{black}{From Date: } `r b_date`  \hspace{5ex}\textcolor{black}{To Date: }  `r e_date`  
\textcolor{black}{Facilty: } `r blt_nm`     \hfill
\textcolor{black}{Total  Amount:} `r total`  \  

\centering


```{r reports, echo=FALSE, results='asis', message=F, warning=F, fig.align='center'}

for ( care_type in unique(rpt_data$Hospital.Service)){
   rpt_sub_data <- rpt_data[rpt_data$Hospital.Service==care_type,]
   names(rpt_sub_data) <- c("Building.name","Hospital.Service","Client Name", "MRN", 
                            "Service From Date", "Service To Date", "Client Rate (Monthly) Rate",
                            "Rate Type")
   print(kable(rpt_sub_data[,c(-1,-2)], row.names = T, longtable = T,                                      # print statement is needed when kable() is in a loop
      format = "latex",booktabs = T) %>% 
      add_header_above(care_type) %>%
      kable_styling(latex_options = c("striped","scale_down",
                                     "hold_postition","repeat_header"),
                                     position = "center",full_width = T,
                                     font_size = 7) %>% 
      footnote(general = "Rate Types: AL - Assisted Living Rate; TAL - Temporary Rate Reduction") 
  )
  
}#end of for loop
```

